On the performance of the MAC model

### 2018-10-31 2018_nips_vigil/smac.tex
typo

>>>>

\begin{table}[]
\centering
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		                & Read Unit               & Write Unit &  Control Unit       & Input Unit & Output Unit & Overall  \\ \hline
		  MAC number of parameters  &  787,969 &  524,800        &    6,822,913          &   15,923,712   &   801,308  &       20,138,526           \\  \hline
		  S-MAC number of parameters  & 263,168  & 262,656       &    6,560,256               &  15,923,712    & 801,308    &       19,089,436           \\  \hline
		 \% parameters reduction  & -67\%  &   -50\%       &      -4\%               &  0\%    & 0\%    &     -5\%              \\  \hline

	\end{tabular}
	\caption{Percentage decrease of the number of parameters by unit between MAC and S-MAC models.}
	\label{results}
\end{table}
